---
title: "Survey_results"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
library(tidyverse)
library(stringr)
library(cld3)
library(stringi)
```

```{r}
path_sam <- "/Users/samuelpflueger/SynologyDrive/01_Uni/02_Master/03_Semester/05_SS21/20_Data_Mining_Seminar/R/Analysis/Eval_Survey_Kopie.csv"

path_tobi <- "/Users/Tobitie/Google Drive/Uni/Master/4. Semester/Data Mining Cup/Evaluvaluation Set_v1.csv"

eval_list <- read_delim(path_sam, delim =";")
#eval_list2 <- read_csv(file = path_sam)
colnames(eval_list) <- tolower(colnames(eval_list)) 
#eval_list <- eval_list %>% rename("title" = "title_option")

survey_orig <- read_csv("survey_59.csv")

survey_long <- survey_orig %>%
  select(-Zeitstempel) %>%
  pivot_longer(cols = 1:20, names_to = "book", values_to = "recommendation") %>%
  arrange(book)

##books
books <- str_split(survey_long$book, " -  ", simplify = TRUE) %>%
  as.data.frame() %>% 
  rename("author" = V1, "title" = V2)

#move SCHLEICH books from author to title
books <- books %>% mutate(
          title = if_else(author == "SCHLEICH® Horse Club - Rätselblock für Pferdefans",
          author, title),
          author = if_else(author == "SCHLEICH® Horse Club - Rätselblock für Pferdefans",
          "", author))
#add itemid as ID
books <- books %>% left_join(eval_list %>% select(title, itemid))

## recommendations
recommendation <- str_split(survey_long$recommendation, " - ", simplify = TRUE) %>%
  as.data.frame() %>% 
  select(-V3) %>% 
  rename("recommendation_author" = V1, "recommendation_title" = V2)

#re-combine SCHLEICH books author and title
recommendation <- recommendation %>% mutate(
    recommendation_title = if_else(grepl('SCHLEICH', recommendation_author),
                      str_c(recommendation_author, recommendation_title, sep = " - "),
                      recommendation_title),
    recommendation_author = if_else(grepl('SCHLEICH', recommendation_author),
                      "",
                      recommendation_author))

#add itemid as ID
recommendation$recommendation_title = str_remove(recommendation$recommendation_title, "^ ")
recommendation <- recommendation %>% left_join(eval_list %>% select(title, itemid), 
                  by = c("recommendation_title" = "title"))

matching_done <- read_delim("matching.csv", delim = ";")

recommendation <- recommendation %>% left_join(matching_done, by = 
            c("recommendation_title" = "recommendation_title")) %>%
            mutate(itemid = if_else(is.na(itemid.x), itemid.y, itemid.x)) %>% 
            select(recommendation_author.x, recommendation_title, itemid) %>% 
            rename(recommendation_author = recommendation_author.x,
                   itemid_rec = itemid)
                           
survey <- cbind(books, recommendation)

```

```{r}
# Prepare data ----------------------------------------------------------------------------------------------------

survey$title = str_remove(survey$title, "^ ")

#colnames(eval_list)[4] <- "title_option"

survey_full <- left_join(survey, eval_list %>% select(-author, -title, -question, -reference), by = c("itemid"))
#survey_full <- left_join(survey, eval_list, by = c("recommendation_title" = "title")) %>% 
  #rename(itemid_rec = itemid)


# Author preparation --------------------------------------------------------------------------------------------------
# how often is same author chosen?
same_author = c()
for(i in 1:20){
  temp <- full_join(survey_full,eval_list) %>%
    filter(ordner == i) %>%
    distinct(author) %>%
    nrow()
  same_author <- cbind(same_author, temp)
}
same_author <- as.data.frame(same_author)
colnames(same_author) <- 1:20

same_author <- as.data.frame(same_author) %>% pivot_longer(cols = 1:20, names_to = "ordner", values_to = "distinct_authors") %>% mutate(ordner = as.double(ordner))

survey_full <- left_join(survey_full, same_author, by = "ordner") 

# ordner 12 missing because no title for those books - add manually
survey_full[(which(is.na(survey_full[,"ordner"]))),"ordner"] <- 12

# Create same author column
survey_full$same_author <- ifelse(survey_full$author == survey_full$recommendation_author, "same_author", "different_author")

# Language preparation --------------------------------------------------------------------------------------------------
# detect if language is same
book_language <- detect_language(eval_list$title) %>%
  as.data.frame() %>%
  rename("language" = ".")

#manually fixing errors and combining data frames
language_fixed <- cbind(eval_list, book_language) %>% select(author, title, language)
language_fixed[7,3] <- "de"
language_fixed[10,3] <- "de"
language_fixed[11,3] <- "en"
language_fixed[12,3] <- "en"
language_fixed[18,3] <- "de"
language_fixed[19,3] <- "de"
language_fixed[22,3] <- "en"
language_fixed[24,3] <- "de"
language_fixed[25,3] <- "en"
language_fixed[26,3] <- "en"
language_fixed[27,3] <- "fr"
language_fixed[28,3] <- "de"
language_fixed[29,3] <- "en"
language_fixed[30,3] <- "en"
language_fixed[32,3] <- "en"
language_fixed[33,3] <- "en"
language_fixed[35,3] <- "en"
language_fixed[36,3] <- "en"
language_fixed[37,3] <- "de"
language_fixed[39,3] <- "de"
language_fixed[40,3] <- "de"
language_fixed[41,3] <- "en"
language_fixed[42,3] <- "en"
language_fixed[43,3] <- "en"
language_fixed[51,3] <- "en"
language_fixed[53,3] <- "en"
language_fixed[56,3] <- "en"
language_fixed[60,3] <- "en"
language_fixed[61,3] <- "en"
language_fixed[63,3] <- "en"
language_fixed[69,3] <- "en"
language_fixed[75,3] <- "en"
language_fixed[77,3] <- "es"
language_fixed[78,3] <- "en"


survey_full <- left_join(survey_full, language_fixed) %>% rename("language_book" = "language")

# find language of the title chosen as best recommender
rec_title <- survey_full %>%
  select(recommendation_title) %>%
  distinct(recommendation_title) 
language_recommendation <- detect_language(rec_title$recommendation_title) %>%
  as.data.frame() %>% 
  rename("language_recommendation" = ".")
rec_title <- cbind(rec_title, language_recommendation)

rec_title$language_recommendation <- c("de","de", NA, "de", "de", "de", "de", "de","de", "de", "es", "es", "es", "de", "fr", "en", "fr", "de", "en", "de","en","en","en","en","en","en","en","en","de","de","de","de","de","de","en","de","en","de","en","en","en","de","fr", "en","en","en","en","de","en","en","en","de","en","en","en","de","de","de","de","en","de")


survey_full <- merge(survey_full, rec_title) %>%
  select(author, title, recommendation_title,recommendation_author:language_recommendation) %>%
  arrange(ordner)

eval_list <- cbind(eval_list,"language" = language_fixed[,"language"])

# Create language proportion columns
same_lang_prop <- data.frame()
for(i in 1:20){
n_distinct_lang <- eval_list %>% filter(ordner == i) %>% distinct(language) %>% nrow() %>% as.integer()
same_lang_prop_i <- rep(n_distinct_lang/4, 4) %>% as.data.frame()
same_lang_prop <- rbind(same_lang_prop, same_lang_prop_i)
}
colnames(same_lang_prop) <- "same_lang_prop"
eval_list <- cbind(eval_list, same_lang_prop)

survey_full <- left_join(survey_full, eval_list)


# Create column with number of distinct languages for each of the 20 questions
unique_languages = c()
for(i in 1:20){
  temp <- eval_list %>% 
    filter(ordner == i) %>%
    distinct(language) %>%
    nrow()
  unique_languages <- append(unique_languages, temp)
}
unique_languages <- data.frame(ordner = 1:20, as.data.frame(unique_languages))


survey_full <- merge(survey_full, unique_languages)
survey_full <- survey_full %>% mutate(same_language = ifelse(language_book == language_recommendation, "same_language", "different_language"))

survey_full <- survey_full[!duplicated(as.list(survey_full))] %>% as.data.frame()
```

# One by one analysis

```{r}

#1 4 same authors, series, same lang
#2 2 same authors, all same lang
#3 2 same authors, book of these diff lang, other two books same lang as main
#4 4 different authors, 2 same lang
#5 4 different authors, all same lang, all same topic
#6 3 same authors, one of these different language as main
#7 4 different authors, 3 different languages, 1 same as main
#8 2 same authors, all same lang
#9 4 diff authors, 2 same lang as main
#10 4 diff authors, all same lang
#11 3 same authors, all same lang
#12 3 same authors, all same lang
#13 2 same authors, all same lang
#14 4 different authors, 3 same lang
#15 4 diff authors, 3 diff lang. 1 same as main
#16 4 diff authors, all same lang
#17 4 diff authors, all same lang
#18 2 same authors, 3 same lang
#19 4 diff authors, 3 same lang
#20 2 same authors, all same lang


# 4 same authors
survey_full %>% filter(ordner == 1) %>% ggplot(aes(recommendation_title)) + geom_histogram(stat = "count") + labs(title = "Only Series - following book chosen most often by far")


# 3 same authors
survey_full %>% filter(ordner %in% c(6,11,12)) %>% ggplot(aes(same_author)) + geom_histogram(stat = "count") + labs(title = "When 2 books of the same author are available,\n people almost exclusively choose the book from the same author")

survey_full %>% filter(ordner %in% c(6,11,12) & same_author == "different_author") %>% ggplot(aes(same_language)) + geom_histogram(stat = "count") # others all same language
# 4/8 most similar cover (ordner 6)
# 4/8 just seem random (ordner 11)


# 2 same authors

survey_full %>% filter(ordner %in% c(2,3,8,13,18,20))%>% ggplot(aes(same_author)) + geom_histogram(stat = "count") + labs(title = "When one book of the same author is available,\n people still tend to choose the book of the same author")
survey_full %>% filter(ordner %in% c(2,3,8,13,18,20) & same_author == "different_author") %>% arrange(ordner, recommendation_author)
#ordner 2 14x more similar cover
#ordner 3 12x same rather than different language
#ordner 8 10x look just like random decision (maybe people want something from a different author?!?)
#ordner 13 7x looks random
#ordner 18 5x seems random (diff language, diff cover), 18 similar content, same lang, similar cover
#ordner 20 4x looks random, 8 seem plausible (also story about animal)

# 4 different authors

survey_full %>% filter(ordner %in% c(4,5,7,10,14,15,16,17,19)) %>% ggplot(aes(same_language)) + geom_histogram(stat = "count") # random guessing would be 7/27 options have different language ~1/4 expected -> not that much over expectation

# Language Distribution
survey_full %>% ggplot(aes(same_language)) + geom_histogram(stat = "count") + facet_wrap(.~same_lang_prop)+labs(title = "language choice behavior by proportion of same language available")

for(i in 1:20){
  plot_i <- survey_full %>% filter(ordner == i) %>% ggplot(aes(recommendation_title)) + geom_histogram(stat = "count") + labs(title = paste("ordner",i))
  print(plot_i)
}

survey_full %>% filter(ordner == 12) %>% ggplot(aes(recommendation_title)) + geom_histogram(stat = "count")
unique(survey_full$ordner)
```




```{r}

## Sam
# questions with no obvious choice: 4 (language),5,7,9,14,15,16,19

##categories
# How many recommendations have the same category as the book?
#save
s1 <- survey_full
#survey_full <- s1

survey_full <- survey_full %>% left_join(eval_list %>% select(topic, itemid), by = c("itemid_rec" = "itemid")) %>% 
  rename(topic_rec = topic.y, topic = topic.x)

survey_full <- survey_full %>% mutate(same_category = ifelse(topic == topic_rec, "yes", "no"))

survey_full %>% filter(is.na(topic_rec)) %>% group_by(recommendation_author) %>% count


#chart: same category
survey_full %>% ggplot(aes(same_category)) + 
  geom_histogram(stat = "count")+
  labs(title = "Same category for all books")
```

#chart: same category, no obvious choice in recommendations
survey_full %>% filter(ordner %in% c(4,5,7,9,14,15,16,19)) %>%
  ggplot(aes(same_category)) + 
  geom_histogram(stat = "count") +
  labs(title = "Same category if no obvious choice is available")


#split categories up
survey_cat <- survey_full %>% select(itemid, itemid_rec, topic, topic_rec, ordner)

survey_cat <- survey_cat %>% mutate(
  t1 = str_sub(topic,1,1),
  t2 = str_sub(topic,1,2),
  t3 = str_sub(topic,1,3),
  t4 = str_sub(topic,1,4),
  t5 = str_sub(topic,1,5),
  t1_rec = str_sub(topic_rec,1,1),
  t2_rec = str_sub(topic_rec,1,2),
  t3_rec = str_sub(topic_rec,1,3),
  t4_rec = str_sub(topic_rec,1,4),
  t5_rec = str_sub(topic_rec,1,5),
  t1_same = ifelse(t1 == t1_rec, "yes", "no"),
  t2_same = ifelse(t2 == t2_rec, "yes", "no"),
  t3_same = ifelse(t3 == t3_rec, "yes", "no"),
  t4_same = ifelse(t4 == t4_rec, "yes", "no"),
  t5_same = ifelse(t5 == t4_rec, "yes", "no")
)

survey_cat %>% filter(ordner == 14) %>% 
  group_by(topic_rec) %>% count %>% 
  ggplot(aes(topic_rec, n))+
  geom_col()

#same topic over 1-5 letters of topic identifier
stat1 <- survey_cat %>% group_by(t1_same, t2_same, t3_same, t4_same, t5_same) %>% 
  count()
  
stat2 <- survey_cat %>% filter(ordner %in% c(4,5,7,9,14,15,16,19)) %>% 
  group_by(t1_same, t2_same, t3_same, t4_same, t5_same) %>% 
  count()

cat_stat <- as_tibble(cbind(stat1[,6], stat2[,6], c("1","2","3","4","5")), .name_repair = "unique")
cat_stat <- cat_stat %>% rename(all = `n...1`, no_obvious = `n...2`, id = `c(\"1\", \"2\", \"3\", \"4\", \"5\")`)
cat_stat <- cat_stat %>% select(id, all, no_obvious)


## cover similarity
survey_color <- survey_full %>% select(ordner, itemid, `main color`, itemid_rec) %>% left_join(
  eval_list %>% select(itemid, `main color`), by = c("itemid_rec" = "itemid"))

#plot color similarity counts for all 20 questions
survey_color %>% group_by(ordner) %>% 
  summarise(same_color = if_else(`main color.x` == `main color.y`, "yes", "no")) %>% 
  group_by(ordner, same_color) %>% count() %>% 
  ggplot(aes(same_color, n))+
  geom_col()+
  facet_wrap(vars(ordner))

#plot for not obvious choice
survey_color %>% filter(ordner %in% c(4,5,7,9,14,15,16,19)) %>%
  group_by(ordner) %>% 
  summarise(same_color = if_else(`main color.x` == `main color.y`, "yes", "no")) %>% 
  group_by(ordner, same_color) %>% count() %>% 
  ggplot(aes(same_color, n))+
  geom_col()+
  facet_wrap(vars(ordner))

#plot for "all no" --> makes no sense, all rec colors differ from book
survey_color %>% filter(ordner %in% c(4,15,16,19)) %>%
  group_by(ordner) %>% 
  summarise(same_color = if_else(`main color.x` == `main color.y`, "yes", "no")) %>% 
  group_by(ordner, same_color) %>% count() %>% 
  ggplot(aes(same_color, n))+
  geom_col()+
  facet_wrap(vars(ordner))

survey_color %>% filter(ordner %in% c(16)) %>%
  group_by(ordner) %>% 
  summarise(same_color = if_else(`main color.x` == `main color.y`, "yes", "no")) %>% 
  group_by(ordner, same_color) %>% count() %>% 
  ggplot(aes(same_color, n))+
  geom_col()+
  facet_wrap(vars(ordner))

survey_color %>% group_by(ordner, itemid_rec) %>% 
  count() %>% filter(ordner %in% c(19)) %>% 
  ggplot(aes(as.factor(itemid_rec), n))+
  geom_col()+
  facet_wrap(vars(ordner), drop = TRUE)

#plot anteil frage nicht beantwortet
survey_color %>% group_by(ordner, is.na(itemid_rec)) %>% 
  count() %>% 
  ggplot(aes(as.factor(ordner),n)) + 
  geom_col(aes(fill = `is.na(itemid_rec)`))

#Sam









